### 2021-04-20 paper/ase21/eval.tex
[ASE21] Updated Table 3
[ASE21] Updating eval

We implemented $\tool$ as an open-source tool~\footnote{The link is anonymized
because of a double-blind review process} in Scala by extending $\jiset$, a
JavaScript IR-based semantics extraction toolchain, with a worklist-based
fixpoint algorithm for type analysis.  Since $\jiset$ cannot automatically
compiles algorithm steps written in an uncommon writing style to $\ires$
instructions, our tool only reports type-related specification bugs detected in
fully compiled abstract algorithms.  For built-in libraries, we only targeted
abstract algorithms of essential built-in objects: \jscode{Array},
\jscode{Object}, \jscode{Function}, \jscode{Math}, \jscode{Proxy}, and objects
for primitive types.

@@

Figure~\ref{fig:stat} shows four statistics of type analysis using $\tool$ for
864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
of flow- and type-sensitive views, (c) the number of worklist iterations, and
(d) the analysis time.  For each version of ECMAScript, \inred{1,999.9}
functions (\stextsf{func}) are analyzed and \inred{1,999.9} functions among them
are fully compiled (\stextsf{full-func}) on average.  Since the compile rules in
$\jiset$ is more suitable for recent versions, the number of fully compiled
functions in older versions are less than in more recent versions.  $\tool$
keeps different abstract environments for each functions divided by flow- and
type-sensitive views.  In the analysis result, \inred{1.3}M views existed for
each version and \inred{1.3}K views existed for each function on average.

We measured performance of $\tool$ based on the number of iterations for
worklist algorithm and the analysis time.  For each version of ECMAScript,
$\tool$ took \inred{300.0} seconds with \inred{19,999.9} iterations of worklist
algorithm on average.  The analysis time consists of \inred{10.0} seconds for
the specification extraction (\stextsf{extract} with gray bars), \inred{340.0}
seconds for the type analysis (\stextsf{analyze} with blue bars), \inred{10.0}
seconds for the bug detection (\stextsf{detect} with red bars).

@@

\begin{table*}
  \centering
  \caption{The analysis precision of $\tool$ without refinement
  (\stextsf{no-refine}), with refinement (\stextsf{refine}), and their
  difference ($\Delta$)}
  \label{table:precision}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{c|c?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l?r@{~}c@{~}l@{~}l|r@{~}c@{~}l@{~}l}
      \multirow{2}{*}{\textbf{Checker}} &
      \multirow{2}{*}{\textbf{Bug Kind}} &
      \multicolumn{24}{c}{
        \textbf{Precision = (\# True Bugs) / (\# Detected Bugs)}
      }\\\cline{3-26} &&
      \multicolumn{8}{c?}{no-refine} &
      \multicolumn{8}{c?}{refine} &
      \multicolumn{8}{c}{$\Delta$}\\

      \myrowc
      {\mr{2}{\stextsf{Reference}}}
      {\me{2}{60}{125}{48.0}} {\me{2}{61}{98}{62.2}} {\me{2}{+1}{-27}{+14.2}}
      {\mr{1}{\stextsf{UnknownVar}}}
      {\me{1}{17}{81}{21.0}} {\me{1}{17}{53}{32.1}} {\me{1}{-}{-28}{+11.1}}

      \smyrowc
      {\mr{1}{\stextsf{Arity}}}
      {\mr{1}{\stextsf{MissParam}}}
      {\me{1}{43}{44}{97.7}} {\me{1}{44}{45}{97.8}} {\me{1}{+1}{+1}{+0.1}}

      \smyrowc
      {\mr{1}{\stextsf{Assertion}}}
      {\mr{1}{\stextsf{Assertion}}}
      {\me{1}{5}{57}{8.8}} {\me{1}{5}{31}{16.1}} {\me{1}{-}{-26}{+7.4}}

      \myrowc
      {\mr{2}{\stextsf{Operand}}}
      {\me{2}{22}{113}{19.5}} {\me{2}{22}{44}{50.0}} {\me{2}{-}{-69}{+30.5}}
      {\mr{1}{\stextsf{NoNumber}}}
      {\me{1}{2}{65}{3.1}} {\me{1}{2}{6}{33.3}} {\me{1}{-}{-59}{+30.3}}

      \myrowh
      {\mr{1}{\stextsf{Abrupt}}}
      {\me{1}{20}{48}{41.7}} {\me{1}{20}{38}{52.6}} {\me{1}{-}{-10}{+11.0}}

We measured the analysis precision based on the number of true bugs in
type-related specification bugs detected by $\tool$.  As described in the
\stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
is \inred{51.7}\% because it detected \inred{190} type-related bugs and
\inred{89} bugs are true bugs among them.  The reference checker detected the
largest number of bugs with \inred{51.7}\% precision; it found \inred{12} true
reference bugs for \inred{32} unknown variables (\stextsf{UnknownVar}) and
\inred{32} already defined variables (\stextsf{DuplicatedVar}). The arity
checker and the assertion checker found \inred{12} missing parameters
(\stextsf{MissParam}) with \inred{90.2}\% precision and \inred{12} assertion
failures (\stextsf{Assertion}) with \inred{90.2}\% precision, respectively.
Finally, the operand checker detected two different kinds of wrong typed operand
bugs: \inred{12} non-numeric operand bugs (\stextsf{NoNumber}) for numeric
operators with \inred{12.3}\% precision and \inred{12} unchecked abrupt
completion bugs (\stextsf{Abrupt}) with \inred{12.3}\% precision.

Moreover, we extended $\tool$ to automatically extract more statistics of
detected true bugs.  \inred{First, we checked that true bugs are created or
resolved by whom as described in Figure~\ref{fig:author}.  Among \inred{89}
true bugs, we cannot automatically know who created \inred{20}
\textit{inherited} bugs, which are created before 2018.  For remaining
\inred{20} bugs, only \inred{20} bugs are created by members of the Ecma
Technical Committee 39 (TC39) but others (\inred{20} bugs) are created by
outside contributors not committee members.  On the other hand, most of them
(\inred{20} bugs) are resolved by the committee members but only \inred{20} bugs
are resolved by non-committee contributors.  Other \inred{14} bugs are newly
found and we will explain their details in Section~\ref{sec:new-bug}.}  Another
statistic of true bugs is Time to Live (TTL) that denotes how many days
specification bugs existed.  Figure~\ref{fig:ttl} describes TTLs of true bugs;
the left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
histogram of TTLs in a logarithmic scale.  The average days of TTL is
\inred{300.0} even though we assume that \inred{20} inherited bugs are created
in January 1, 2018.  The maximum length of TTL is \inred{1,000} and the
corresponding bug is inherited and not yet resolved in the latest version.  We
manually investigated its creation time in the history of the official
repository, and we discovered that it was created at the initial commit of the
open development process in September 22, 2015.  It means that the bug actually
existed for \inred{3,000} days.

@@

\begin{table*}
  \centering
  \caption{Type-related specification bugs newly detected by $\tool$ in the
  official draft of ECMAScript 2021 (ES12).}
  \label{table:new-bug}
  \resizebox{\textwidth}{!}{%
  \begin{tabular}{@{}c@{~}?c|@{~}c@{~}|l|c|@{~}c@{~}|@{~}c@{~}|@{~}r@{}}
    \multicolumn{1}{@{}c?}{\textbf{Name}} &
    \multicolumn{1}{c}{\textbf{Feature}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{\#}} &
    \multicolumn{1}{c}{\textbf{Description}} &
    \multicolumn{1}{@{~}c@{~}}{\textbf{Checker}} &
    \multicolumn{1}{@{}c}{\textbf{Created}} &
    \multicolumn{1}{@{}c}{\textbf{Resolved}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{TTL}}\\\specialrule{.1em}{.0em}{.0em}

    ES12-1 &
    Switch &
    3 &
    \makecell[l]{
        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already \\
        defined in algorithms for \jscode{case} blocks of \jscode{switch}
        statements.
    } &
    \stextsf{Reference} &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-2 &
    Try &
    3 &
    \makecell[l]{
        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already \\
        defined in algorithms for \jscode{try} statements.
    } &
    \stextsf{Reference} &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-3 &
    Arguments &
    1 &
    \makecell[l]{
        A variable \code{index} is already defined in
        \textbf{CreateMappedArgumentsObject}.
    } &
    \stextsf{Reference} &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-4 &
    Array &
    2 &
    \makecell[l]{
        A variable \code{succeeded} is already defined in algorithms for
        \jscode{Array} objects.
    } &
    \stextsf{Reference} &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-5 &
    Async &
    1 &
    \makecell[l]{
        A variable \code{value} is already defined in \textbf{Evaluation} for
        \jscode{yield} expressions.
    } &
    \stextsf{Reference} &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-6 &
    Class &
    1 &
    \makecell[l]{
        A variable \code{ClassHeritage} is not defined in \textbf{Contains}
        \\ for tails of \jscode{class} declarations.
    } &
    \stextsf{Reference} &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-7 &
    Branch &
    1 &
    \makecell[l]{
        A variable \code{Statement} is not defined in \textbf{EarlyErrors} for
        \jscode{if} statement.
    } &
    \stextsf{Reference} &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-8 &
    Arguments &
    2 &
    \makecell[l]{
        Abrupt completions are used in \textbf{DefineOwnProperty} and
        \textbf{GetOwnProperty} \\ for \jscode{arguments} objects without any
        checks.
    } &
    \stextsf{Operand} &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\
  \end{tabular}
  }
  \vspace*{-1.5em}
\end{table*}

>>>>

\begin{table*}
  \centering
  \caption{The analysis precision of $\tool$ without refinement
  (\stextsf{no-refine}), with refinement (\stextsf{refine}), and their
  difference ($\Delta$)}
  \label{table:precision}
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{c|c?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r?r@{~}c@{~}r@{~}l@{}r|r@{~}c@{~}r@{~}l@{}r}
      \multirow{2}{*}{\textbf{Checker}} &
      \multirow{2}{*}{\textbf{Bug Kind}} &
      \multicolumn{30}{c}{
        \textbf{Precision = (\# True Bugs) / (\# Detected Bugs)}
      }\\\cline{3-32} &&
      \multicolumn{10}{c?}{no-refine} &
      \multicolumn{10}{c?}{refine} &
      \multicolumn{10}{c}{$\Delta$}\\

      \myrowc
      {\mr{2}{\stextsf{Reference}}}
      {\me{2}{60}{125}{48.0}} {\me{2}{61}{98}{62.2}} {\me{2}{+1}{-27}{+14.2}}
      {\mr{1}{\stextsf{UnknownVar}}}
      {\me{1}{17}{81}{21.0}} {\me{1}{17}{53}{32.1}} {\me{1}{}{-28}{+11.1}}

      \smyrowc
      {\mr{1}{\stextsf{Arity}}}
      {\mr{1}{\stextsf{MissParam}}}
      {\me{1}{4}{4}{100.0}} {\me{1}{4}{4}{100.0}} {\me{1}{}{}{}}

      \smyrowc
      {\mr{1}{\stextsf{Assertion}}}
      {\mr{1}{\stextsf{Assertion}}}
      {\me{1}{5}{57}{8.8}} {\me{1}{5}{31}{16.1}} {\me{1}{}{-26}{+7.4}}

      \myrowc
      {\mr{2}{\stextsf{Operand}}}
      {\me{2}{22}{113}{19.5}} {\me{2}{22}{44}{50.0}} {\me{2}{}{-69}{+30.5}}
      {\mr{1}{\stextsf{NoNumber}}}
      {\me{1}{2}{65}{3.1}} {\me{1}{2}{6}{33.3}} {\me{1}{}{-59}{+30.3}}

      \myrowh
      {\mr{1}{\stextsf{Abrupt}}}
      {\me{1}{20}{48}{41.7}} {\me{1}{20}{38}{52.6}} {\me{1}{}{-10}{+11.0}}

We implemented $\tool$ as an open-source tool~\footnote{The link is anonymized
because of a double-blind review process} in Scala by extending $\jiset$, a
JavaScript IR-based semantics extraction toolchain, with a worklist-based
fixpoint algorithm for type analysis.  Since $\jiset$ cannot automatically
compiles algorithm steps written in an uncommon writing style to $\ires$
instructions, our tool only reports type-related specification bugs detected in
fully compiled abstract algorithms.  For built-in libraries, we only targeted
abstract algorithms of essential built-in objects: \jscode{Array},
\jscode{Object}, \jscode{Function}, \jscode{Math}, \jscode{Proxy}, and objects
for JavaScript primitive types.

@@

Figure~\ref{fig:stat} shows four statistics of type analysis using $\tool$ for
864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
of flow- and type-sensitive views, (c) the number of worklist iterations, and
(d) the analysis time.  For each version of ECMAScript, \inred{1,689.6}
functions (\stextsf{analyzed}) are analyzed and \inred{1,570.0} functions among
them are fully compiled (\stextsf{compiled}) on average.  Since ECMAScript has
gradually evolved for three years, \inred{1,357} out of \inred{1,490} analyzed
functions are fully compiled at the first version in 2018 but \inred{1741} out
of \inred{1,863} analyzed functions are fully compiled in the latest version.
$\tool$ divides functions to flow- and type-sensitive views.  On average,
\inred{91.2}K views existed for each version and \inred{53.9} views existed for
each function.

We measured performance of $\tool$ based on the number of iterations for
worklist algorithm and the analysis time.  For each version of ECMAScript,
$\tool$ took \inred{136.0} seconds with \inred{298.8}K iterations of worklist
algorithm on average.  The average analysis time consists of \inred{8.0} seconds
for the specification extraction (\stextsf{extract} with gray bars),
\inred{127.0} seconds for the type analysis (\stextsf{analyze} with blue bars),
\inred{0.7} seconds for the bug detection (\stextsf{detect} with red bars).

@@

We measured the analysis precision based on the number of true bugs in
type-related specification bugs detected by $\tool$.  As described in the
\stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
is \inred{52.0}\% because it detected \inred{177} type-related bugs and
\inred{92} bugs are true bugs among them.  The reference checker detected the
largest number of bugs with \inred{62.2}\% precision; it found \inred{61} true
reference bugs for \inred{17} unknown variables (\stextsf{UnknownVar}) and
\inred{44} already defined variables (\stextsf{DuplicatedVar}). The arity
checker and the assertion checker found \inred{4} missing parameters
(\stextsf{MissParam}) with \inred{100.0}\% precision and \inred{5} assertion
failures (\stextsf{Assertion}) with \inred{16.1}\% precision, respectively.
Finally, the operand checker detected two different kinds of wrong typed operand
bugs: \inred{2} non-numeric operand bugs (\stextsf{NoNumber}) for numeric
operators with \inred{33.3}\% precision and \inred{20} unchecked abrupt
completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.

Moreover, we extended $\tool$ to automatically extract more statistics of
detected true bugs.  \inred{First, we checked that true bugs are created or
resolved by whom as described in Figure~\ref{fig:author}.  Among \inred{92}
true bugs, \inred{47} bugs are \textit{inherited}, which means that they are
created before 2018, and \inred{14} bugs are newly found

\inred{20} bugs, only \inred{20} bugs are created by members of the Ecma
Technical Committee 39 (TC39) but others (\inred{20} bugs) are created by
outside contributors not committee members.  On the other hand, most of them
(\inred{20} bugs) are resolved by the committee members but only \inred{20} bugs
are resolved by non-committee contributors.  Other \inred{14} bugs are newly
found and we will explain their details in Section~\ref{sec:new-bug}.}  Another
statistic of true bugs is Time to Live (TTL) that denotes how many days
specification bugs existed.  Figure~\ref{fig:ttl} describes TTLs of true bugs;
the left chart (Figure~\ref{fig:ttl}(a)) depicts their periods sorted by their
creation time, and the right chart (Figure~\ref{fig:ttl}(b)) depicts the
histogram of TTLs in a logarithmic scale.  The average days of TTL is
\inred{300.0} even though we assume that \inred{20} inherited bugs are created
in January 1, 2018.  The maximum length of TTL is \inred{1,000} and the
corresponding bug is inherited and not yet resolved in the latest version.  We
manually investigated its creation time in the history of the official
repository, and we discovered that it was created at the initial commit of the
open development process in September 22, 2015.  It means that the bug actually
existed for \inred{3,000} days.

@@

\begin{table*}
  \centering
  \caption{Type-related specification bugs newly detected by $\tool$ in the
  official draft of ECMAScript 2021 (ES12).}
  \label{table:new-bug}
  \resizebox{\textwidth}{!}{%
  \begin{tabular}{@{}c@{~}?c|@{~}c@{~}|l|c|@{~}c@{~}|@{~}r@{}}
    \multicolumn{1}{@{}c?}{\textbf{Name}} &
    \multicolumn{1}{c}{\textbf{Feature}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{\#}} &
    \multicolumn{1}{c}{\textbf{Description}} &
    \multicolumn{1}{@{~}c@{~}}{\textbf{Checker}} &
    \multicolumn{1}{@{}c}{\textbf{Created}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{TTL}}\\\specialrule{.1em}{.0em}{.0em}

    ES12-1 &
    Switch &
    3 &
    \makecell[l]{
        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already \\
        defined in algorithms for \jscode{case} blocks of \jscode{switch}
        statements.
    } &
    \stextsf{Reference} &
    2015-09-22 &
    1,996 days\\\hline

    ES12-2 &
    Try &
    3 &
    \makecell[l]{
        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already \\
        defined in algorithms for \jscode{try} statements.
    } &
    \stextsf{Reference} &
    2015-09-22 &
    1,996 days\\\hline

    ES12-3 &
    Arguments &
    1 &
    \makecell[l]{
        A variable \code{index} is already defined in
        \textbf{CreateMappedArgumentsObject}.
    } &
    \stextsf{Reference} &
    2015-09-22 &
    1,996 days\\\hline

    ES12-4 &
    Array &
    2 &
    \makecell[l]{
        A variable \code{succeeded} is already defined in algorithms for
        \jscode{Array} objects.
    } &
    \stextsf{Reference} &
    2015-09-22 &
    1,996 days\\\hline

    ES12-5 &
    Async &
    1 &
    \makecell[l]{
        A variable \code{value} is already defined in \textbf{Evaluation} for
        \jscode{yield} expressions.
    } &
    \stextsf{Reference} &
    2015-09-22 &
    1,996 days\\\hline

    ES12-6 &
    Class &
    1 &
    \makecell[l]{
        A variable \code{ClassHeritage} is not defined in \textbf{Contains}
        \\ for tails of \jscode{class} declarations.
    } &
    \stextsf{Reference} &
    2015-09-22 &
    1,996 days\\\hline

    ES12-7 &
    Branch &
    1 &
    \makecell[l]{
        A variable \code{Statement} is not defined in \textbf{EarlyErrors} for
        \jscode{if} statement.
    } &
    \stextsf{Reference} &
    2015-09-22 &
    1,996 days\\\hline

    ES12-8 &
    Arguments &
    2 &
    \makecell[l]{
        Abrupt completions are used in \textbf{DefineOwnProperty} and
        \textbf{GetOwnProperty} \\ for \jscode{arguments} objects without any
        checks.
    } &
    \stextsf{Operand} &
    \inred{2015-09-22} &
    \inred{1,996 days}\\
  \end{tabular}
  }
  \vspace*{-1.5em}
\end{table*}
